---
title: "p8105_hw5_qz2492"
author: "qz2492"
date: "2022-11-17"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


### Due date

Due: November 16 at 11:59pm. 

### Points

| Problem         | Points    |
|:--------------- |:--------- |
| Problem 0       | 20        |
| Problem 1       | --        |
| Problem 2       | 40        |
| Problem 3       | 40        |
| Optional survey | No points |


### Problem 0

This "problem" focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. This was not prepared as a GitHub repo.

```{r load_libraries}
library(tidyverse)
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 


## Problem 2

### Describe the raw data
```{r}
homicide = read_csv('data/homicide-data.csv')
```
There are 52179 observations and 12 variables, including `uid`, `reported_date`, `victim_last`, `victim_first`, `victim_race`, `victim_age`, `victim_sex`, `city`, `state`, `lat`, `lon` and `disposition`.

### Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides 

```{r}
uns_homi = homicide %>%
  mutate(city_state = str_c(city, state, sep = "_")) %>%
  group_by(city_state) %>%
  summarize(
    n_obs = n(),
    unsolved =  sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  ) %>%
  filter(city_state != "Tulsa_AL") # exclude wrong data
  
```

### For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
Balt_uns_homi = filter(uns_homi, city_state == "Baltimore_MD")
Balt_test =  prop.test(x = Balt_uns_homi$unsolved, n = Balt_uns_homi$n_obs)
save(Balt_test, file = "Balt_test.RData")
Balt_test %>%
  broom::tidy() %>%
  select(estimate, conf.low, conf.high)
```
### Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
res_homi = uns_homi %>%
  mutate(
    prop_res = map2(.x = unsolved, .y = n_obs,  ~ broom::tidy(prop.test(x = .x, n = .y)))
  ) %>%
  unnest(prop_res) %>%
  select(city_state, estimate, conf.low, conf.high)
```

### Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
res_homi %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = estimate, y = city_state)) + 
  geom_point() +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
  labs(title = "Unsolved Homicides Estimates and CIs for each City")
```

## Problem 3

### n = 30, sigma = 5, firstly, μ = 0

```{r}
# simulation function
simulate_for_t = function(n = 30, mu = 0, sigma = 5){
  x = rnorm(n = n, mean = mu, sd = sigma)
  result = t.test(x) %>% broom::tidy()
  
  result
}

# generate 5000 datasets for mu = 0
t_test_0 = vector("list", 5000)
for (i in 1:5000) {
  t_test_0[[i]] = simulate_for_t()
}
t_test_0 %>% 
  bind_rows() %>%
  select(estimate, p.value) %>%
  head(5)
```

### Repeat the above for μ={0,1,2,3,4,5,6}

```{r}
t_test_all = 
  tibble(
    mu = c(0, 1, 2, 3, 4, 5, 6)) %>% 
      mutate(
        output_list = map(.x = mu, ~rerun(5000, simulate_for_t(mu = .x))),
        output_df = map(output_list, bind_rows)
      ) %>% 
      unnest(output_df) %>% 
      select(-output_list)
```

### Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

```{r}
t_test_all %>% 
  group_by(mu) %>% 
  mutate(
    power = sum(p.value < 0.05)/ n()
  ) %>% 
  janitor::clean_names() %>% 
  ggplot(aes(x = mu, y = power)) + 
  geom_point() + 
  geom_line() +
  labs(
    title = "The association between effect size and power",
    x = "True value of Mu",
    y = "Power of the Test"
  )
```

The power of the test increases as the true value of μ increases, and it almost reaches 1 when μ equals 5.

### Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

```{r}
# in all samples
t_test_all %>% 
  group_by(mu) %>% 
  mutate(
    avg_mu = mean(estimate)
  ) %>% 
  ggplot(aes(x = mu, y = avg_mu)) + 
  geom_point() +
  geom_line() +
  labs(
    x = "True value of μ",
    y = "Average Estimate of μ",
    title = "True μ vs. Average Estimate of μ(all samples)")
```

```{r}
# only in samples for which the null was rejected
t_test_all %>% 
  group_by(mu) %>% 
  filter(p.value < 0.05) %>%
  mutate(
    avg_mu = mean(estimate)
  ) %>% 
  ggplot(aes(x = mu, y = avg_mu)) + 
  geom_point() +
  geom_line() +
  labs(
    x = "True value of μ",
    y = "Average Estimate of μ",
    title = "True μ vs. Average Estimate of μ(null rejected samples)")
```

In comparison between two plots, we can know that the sample average of μ across tests for which the null is rejected does not equal to the true value of μ. Or we can say that when the true value of μ is relatively large(5,6), the two μs are approximately the same size, but the gap between them is rather large when the true μ is smaller. This is because the effect size has a great influence on the power of test, we must be careful with it.